Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-18 journal/article.tex
Large scale

Proceeding a workshop at XP2013 Dingsøyr et al. \cite{Dingsoyr2013} compiled a
description of the definition of large scale. Dingsøyr et al. describe that
at the XP2013 workshop the most common view on large scale was the involvment of
many people. Dingsøyr et al. also conducted a brief literature search to
identify what definitions on large scale are used. The results showed that
large scale had been regadred in terms of size in persons or teams, project
budget, code base size, and project duration. Paasivaara et al.
\cite{Paasivaara2008} referred to an organization of 40 people and 7 teams.
Berger and Beynon-Davies \cite{Berger2009} present the project cost of over £10
million as a factor of large scale, but also highlight a team size of over 50
people. A product with a code base size of over 5 million lines of code was
considered to represent a large scale development effort by Petersen and Wohlin
\cite{Petersen2010}. A project time of 2 years was considered as a factor of
large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a project scope
of 60-80 features.

>>>>

Proceeding a workshop at XP2013 \cite{Dingsoyr2013a} Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
Dingsøyr et al. describe that at the XP2013 workshop the most common view on
large scale was the involvment of many people \cite{Dingsoyr2013b}. Dingsøyr et
al. conducted a brief literature search to identify what definitions on large
scale are used. The results showed that large scale had been regadred in terms
of size in persons or teams, project budget, code base size, and project
duration.
Paasivaara et al. \cite{Paasivaara2008} referred to an organization of 40 people
and 7 teams. Berger and Beynon-Davies \cite{Berger2009} present the project cost
of over £10 million as a factor of large scale, but also highlight a team size
of over 50 people. A product with a code base size of over 5 million lines of
code was considered to represent a large scale development effort by Petersen
and Wohlin \cite{Petersen2010}. A project time of 2 years was considered as a
factor of large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a
project scope of 60-80 features.
